Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-26 paper/paper.tex
Add abstract.

\section*{Abstract}
\emph{Will write this when the paper is done}

>>>>

\section*{Abstract}
\emph{The problem of inaccurate item-item similarity estimates due to a lack of
data is explored within the context of collaborative filtering. An off-line
experiment that evaluates the performance of similarity estimators is described.
Two novel item-item similarity estimators are described and analyzed. The first
is based on a model of noisy similarity score generation and proves effective at
estimating both future Pearson correlations and cosine similarities. The second
models noisy ratings as generated by similarity score dependent distributions.
Using the notion of user predictivity, accurate estimates of future Pearson
correlation are made.}
